%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

%-------------------------
% Packages Used

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

%-------------------------
% Main Styling

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Prevents overfull hbox and vbox
%\hbadness=10000
%\hfuzz=50pt
%\vbadness=10000
%\vfuzz=50pt

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

%\usepackage[top=25pt, bottom = 25pt, left= 40pt, right  = 40pt]{geometry}

%\hypersetup{
%    colorlinks,%
%    citecolor=black,%
%    filecolor=black,%
%    linkcolor=black,%
%    urlcolor=black 
%}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-------------------------
% Custom commands

% Sections formatting
\titleformat{\section}{
\vspace{-10pt}
\scshape\raggedright\large }{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\reslistitem}[1]{\small{\item #1 \vspace{-6pt}}}

\newcommand{\ressubheadingold}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubheading}[4]{\textbf{#3, #1} \hfill \small{#2, #4} \vspace{-8pt}}

\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
    \textbf{\href{http://www.cc.gatech.edu/~sbajaj9/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabhbajaj@gatech.edu}{sourabhbajaj@gatech.edu}\\
    \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : \hspace{33pt} +1-404-834-4787
    \end{tabular*}
\\}

%-------------------------------------------

%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%\renewcommand\labelitemi{}
%\newcommand{\localtextbulletone}{\textcolor{gray}{\raisebox{.45ex}{\rule{.6ex}{.6ex}}}}
%\renewcommand{\labelitemi}{\localtextbulletone} 

%-------------------------------------------
\mywebheader
%\begin{center}
%\textsc{\LARGE{Sourabh Bajaj}} \\
%{\large\Telefon} +1-(404)-834-4787 \hfill {\large\Mundus} http://sb2nov.github.com \hfill {\large\Letter} \href{mailto:sourabhbajaj@gatech.edu}{sourabhbajaj@gatech.edu} 
%\end{center}

%-------------------------------------------
%\section{Objective}
%    \begin{itemize}
%        \reslistitem{ To obtain a full time position in the field of Computer Science, starting January 2014. }
%    \end{itemize}
    
%-------------------------------------------
\section{Education}
    \begin{itemize}
        \item
            \ressubheadingold{\href{http://www.gatech.edu}{Georgia Institute of Technology}}{Atlanta, GA}{\href{http://www.cc.gatech.edu}{Master of Science in Computer Science}; 
            {GPA: 4.00}}{Aug. 2012 -- Dec. 2013}
        \item
            \ressubheadingold{\href{http://www.bits-pilani.ac.in}{Birla Institute of Technology and Science}}{Pilani, India}{\href{http://www.bits-pilani.ac.in/pilani/ElectricalElectronicsInstrumentation/Home}{Bachelor of Engineering in Electrical and Electronics}; 
            {GPA: 3.66 (9.15/10.0)}}{Aug. 2008 -- July. 2012} 
    \end{itemize} % End Education list

%-------------------------------------------
\vspace{1pt}

%-------------------------------------------
\section{Programming Skills}
    \begin{itemize}
        \reslistitem{ C, C++, Python, Matlab, GIT, Latex, JavaScript, D3, Hadoop, SQL, JQuery, HTML, CSS, Java, R, SVN}
    \end{itemize}

%-------------------------------------------
\vspace{1pt}
%-------------------------------------------
\section{Work Experience}
\begin{itemize}
        \item 
            \ressubheading{\href{http://www.coursera.org}{Coursera}}{Mountain View, CA}{Software Engineer - Analytics}{Jan 2014 - Present}
                { \small
                \begin{itemize}
                    \resitem{Developer in the analytics team at Coursera. I contribute to the backend infrastructure for data analytics as well as to analyzing student activity to help create a better teaching experience.}
                \end{itemize}
                }
        \item 
            \ressubheading{\href{http://www.lucenaresearch.com}{Lucena Research}}{Atlanta, GA}{Software Developer}{Summer 2012 and 2013}
                { \small
                \begin{itemize}
                    \resitem{Developer of python backend of QuantDesk, a web application for use by hedge fund managers.}
                    \resitem{Developed proprietary algorithms for portfolio hedging,  portfolio optimization and price forecasting. Designed algorithm based on machine learning and pattern recognition on financial data. Also creating a strategy backtesting engine used for simulating and backtesting strategies.}
                    \resitem{Consulting and portfolio management of several hedgefunds and market investors.}
                \end{itemize}
                }
        \item 
            \ressubheading{\href{http://www.analog.com}{Analog Devices}}{Bangalore, India}{Software Developer Intern}{Summer 2011}
                { \small
                \begin{itemize}
                    \resitem{Designed a low cost prototype to control a 3D image in real-time based on motion capture using MEMS.}
                \end{itemize}
                }
        \item 
            \ressubheading{\href{http://www.larsentoubro.com}{Larsen and Toubro}}{Mumbai, India}{Project Engineer Intern}{Summer 2010}
                { \small
                \begin{itemize}
                    \resitem{Designed and programmed PLC panels for automation of a 600km pipeline, under the Gas Authority of India.}
                \end{itemize}
                }
    \end{itemize} % End Work Experience

%-------------------------------------------
\vspace{1pt}
%-------------------------------------------
\section{Research and Teaching Experience}
    \begin{itemize}
        \item 
            \ressubheading{\href{https://www.coursera.org/course/compinvesting1}{Coursera}}{Atlanta, GA}{Teaching Assistant}{Aug 2012 -- Dec 2013}
                { \small
                \begin{itemize}
                    \resitem{Course: Computational Investing - I. The course had more than 100,000 students enrolled. The class was featured on the 11 Alive News and the Atlanta Journal Constitution.}
                \end{itemize}
                }
        \item           
            \ressubheading{\href{https://www.gatech.edu}{Georgia Tech}}{Atlanta, GA}{Graduate Research Assistant}{Jan 2012 -- Dec 2013}
                { \small                
                \begin{itemize}
         \resitem{Research on application of machine learning and statistics for portfolio hedging and trading algorithms. Focus on creating low-risk, continues-return based trading strategies. Also developer of the python library QSTK.}
                    \resitem{Teaching assistant for the class Machine Learning for Trading. Involved in creating assignment, exams and conducting recitation sessions.}
                \end{itemize}
                }
        \item 
            \ressubheading{\href{http://www.bits-pilani.ac.in}{BITS Pilani}}{Pilani, India}{Professional Assistant}{Aug 2009 -- Dec 2012}
                { \small
                \begin{itemize}
                    \resitem{Teaching assistant for Computer programming-1 and Engineering graphics courses. Undergraduate researcher in the electrical and electronics department, worked on image and video processing algorithms.
                \end{itemize}
                }
    }\end{itemize}  % End Experience list

%-------------------------------------------
\vspace{-8pt}

%-------------------------------------------
\section{Academic Projects}
    \begin{itemize}
          \reslistitem{\textbf{QuantSoftware Toolkit}: Open source python library for financial data analysis and machine learning for finance.}
	 \reslistitem{\textbf{Portfolio Replication}: Developing a replication algorithm, using machine learning and statistical methods for risk minimization, creating survivor bias free data, duplicating returns of hedge funds.}
	\reslistitem{\textbf{Github Visualization}: A visualization tool created using D3js to visualize log data for an organization on Github. Helps in analyzing activity trends in developer and project activity over time.}
	\reslistitem{\textbf{Event Connect}: An android as well as a web app designed to organize events and activities across campus.  }
	\reslistitem{\textbf{PageRank - Hadoop Vs Giraph}: A comparitive study b/w vanilla hadoop and Giraph for graph processing. }
	\reslistitem{\textbf{Recommendation System}: Developed music and movie recommender system using collaborative filtering.}
	\reslistitem{\textbf{Dimensionality Reduction: PCA, KPCA, ICA}: Comparative analysis for various classification problems.}
    \end{itemize}

%-------------------------------------------
\end{document}

%-------------------------------------------
\vspace{1pt}

%-------------------------------------------
\section{Publications}
    \begin{itemize}
	\reslistitem{Sourabh Bajaj, \textit{3D Image control using MEMS sensors for Teaching Purposes}, 4th IEEE 4th ICECT, 2012.}
	\reslistitem{Sourabh Bajaj and D Kumar, \textit{Novel Approach to 3D gaming using MEMS Sensors}, 4th IEEE 4th ICECT, 2012.}
        \reslistitem{Sourabh Bajaj and DKumar, \textit{Real time 3D Anaglyph Image Control Using MEMS Sensors}, 7th ICMENS, 2011.}
    \end{itemize}

%-------------------------------------------
\vspace{1pt}

%-------------------------------------------
\section{Involvement}
    \begin{itemize}
        \reslistitem{Graduate Student Senate for computer science, 2012-2013}
        \reslistitem{Reviewer for International Conference of Signal Processing and Control, 2012}
        \reslistitem{Vice president of IEEE student chapter at BITS Pilani, 2011.}
        \reslistitem{Student in-charge of Anti-Ragging committee of boys hostel, 2011.}
    \end{itemize}
