% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009-2012 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com 
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

% GENERAL NOTE:  There may be some notes specific to myself.  If you're only interested in my LaTeX source or it doesn't make sense, please disregard it.

\documentclass[letterpaper,9pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=black     % can put red here to better visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.30}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.575in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{ \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------

\begin{document}
\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
    \textbf{\href{http://www.cc.gatech.edu/~sbajaj9/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabhbajaj@gatech.edu}{sourabhbajaj@gatech.edu}\\
    \href{http://www.cc.gatech.edu/~sbajaj9/}{http://www.cc.gatech.edu/{\raise.17ex\hbox{$\scriptstyle\sim$}}sbajaj9/} & Mobile : \hspace{30pt} +1-404-834-4787
    %{\footnotesize \texttt{301, 10th St. Atlanta, GA}} & +1-404-834-4787 
    %\href{http://www.derekhildreth.com}{http://derekhildreth.com} \\
    \end{tabular*}
\\
\vspace{0.1in}}

\mywebheader
%%%%%%%%%%%%%%%%%%%%%%
\vspace{8pt}
\resheading{Objective}
	\vspace{-13pt}
	\begin{itemize}
		\item{ To obtain a full time position in the field of Computer Science, starting January 2014. }
%		\vspace{-3pt}
%		\item{\textbf{Familiar: } \small R, Java, HTML, CSS. }
	\end{itemize} % End Skills list
	
%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
	\vspace{-10pt}
	\begin{itemize}
		\item
			\ressubheading{\href{http://www.gatech.edu}{Georgia Institute of Technology}}{Atlanta, GA}{\href{http://www.cc.gatech.edu}{Master of Science in Computer Science}; 
			%\href{http://www.derekhildreth.com/portfolio/unofficial_transcript.pdf}
			{GPA: 4.00}}{Aug. 2012 -- Dec. 2013*}
				{ \footnotesize
				\begin{itemize}
%					\resitem{\small \textbf{Available for Internship: Summer, 2013; Graduation follows Internship.}}
					\resitem{\small Courses: Computability and Algorithms, Web Search and Text Mining, Machine Learning, Artificial Intelligence, Computer Vision and Machine Learning for Trading, Multi-robot systems}
				\end{itemize}
				}
		\item
			\ressubheading{\href{http://www.bits-pilani.ac.in}{Birla Institute of Technology and Science}}{Pilani, India}{\href{http://www.bits-pilani.ac.in/pilani/ElectricalElectronicsInstrumentation/Home}{Bachelor of Engineering in Electrical and Electronics}; 
			%\href{http://www.derekhildreth.com/portfolio/unofficial_transcript.pdf}
			{GPA: 3.66 (9.15/10.0)}}{Aug. 2008 -- July. 2012}
				{ \small
				\begin{itemize}
					\resitem{Courses: Digital Electronics, Data Structures, Computer Programming, Linear Algebra, Calculus, Image Processing, Analog Electronics, Computer Networks and Control Systems.}
	\end{itemize} % End Education list
}\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%
%\vspace{2pt}
\resheading{Programming Skills}
	\vspace{-13pt}
	\begin{itemize}
		\item{\textbf{Proficient: }\small Python, C, C++, Matlab, LaTeX, GIT, SVN, HTML. \hfill \textbf{Familiar: }\small R, Java, Scripting, CSS, MySQL. }
		\vspace{-6pt}
		\item{\textbf{Python Packages: }\small Numpy, Scipy, Pandas, Matplotlib, Dateutil, QSTK, Sklearn, Recsys, Cvxopt, PyQT4 etc. }
%		\vspace{-3pt}
%		\item{\textbf{Familiar: } \small R, Java, HTML, CSS. }
	\end{itemize} % End Skills list
%\vspace{2pt}
%\end{document}

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Industry Experience}
	\vspace{-13pt}
	\begin{itemize}
		\item 
			\ressubheading{\href{http://www.lucenaresearch.com}{Lucena Research}}{Atlanta, GA}{Software Developer \& Quantitative Analyst}{May. 2013 -- Aug. 2013}
				{ \small
				\begin{itemize}
					\resitem{Full-stack engineer at an early-stage start-up that applies machine learning and to financial markets.}
					\resitem{Development of propriatery price forecasting algorithm for intraday trading. Application of pattern recognition and machine learning algorithms for prediction analysis.}
					\resitem{Creating a strategy backtesting engine used for simulating strategies created using Lucena's web application.}
				\end{itemize}
				}
		\item 
			\ressubheading{\href{http://www.lucenaresearch.com}{Lucena Research}}{Atlanta, GA}{Software Developer \& Quantitative Analyst}{May. 2012 -- Aug. 2012}
				{ \small
				\begin{itemize}
					\resitem{Full-stack engineer at an early-stage start-up that applies machine learning and to financial markets.}
					\resitem{Core developer of the python backend of QuantDesk, a web application for use by hedge fund managers. Developed proprietary algorithms for portfolio hedging and portfolio optimization.}
					\resitem{Responsible for direct consulting and portfolio management of several clients}
				\end{itemize}
				}
		\item 
			\ressubheading{\href{http://www.analog.com}{Analog Devices}}{Bangalore, India}{Software Developer Intern}{May. 2011 -- Aug. 2011}
				{ \small
				\begin{itemize}
					\resitem{Designed a low cost prototype to control a stereo image in realtime based on motion capture using inputs from multiple Accelerometers and Gyroscopes. Applicaton targeted towards being used in classroom teaching.}
					\resitem{Project resulted in several publications at completion.}
				\end{itemize}
				}
		\item 
			\ressubheading{\href{http://www.larsentoubro.com}{Larsen and Toubro}}{Mumbai, India}{Project Engineer Intern}{May. 2010 -- Aug. 2010}
				{ \small
				\begin{itemize}
					\resitem{Designed, programmed and tested PLC panels for automation of a 600km Gas Pipeline. This project was funded by the Gas Authority of India.}
					\resitem{Designs created are currently being used in the pipeline.}
				\end{itemize}
				}
	\end{itemize}  % End Experience list
\vspace{3pt}
%%%%%%%%%%%%%%%%%%%%%%
\resheading{Research Experience}
	\vspace{-13pt}
	\begin{itemize}
		\item			
			\ressubheading{\href{https://www.gatech.edu}{Georgia Institute of Technology}}{Atlanta, GA}{Graduate Research Assistant}{Aug. 2012 -- Present}
				{ \small				
				\begin{itemize}
					\resitem{Research assistant under Dr. Tucker Balch, Application of machine learning and statistics for portfolio hedging and trading algorithms. Involved in creating algorithms for portfolio replication to be used in creating survivor bias free data, replication of hedge fund returns etc.}
				\end{itemize}
				}
			\vspace{-12pt}	
			\ressubheading{}{}{Research Intern}{Jan. 2012 -- Aug 2012}
				{ \small				
				\begin{itemize}
					\resitem{Developed a modern portfolio theory based optimizer, for optimal portfolio allocations for max return and minimum risk. Also created a visualization tool for analysis of various technical indicators.}
				\end{itemize}
				}
		\item 
			\ressubheading{\href{http://www.bits-pilani.ac.in}{Birla Institute of Technology and Science}}{Pilani, India}{Research Assistant}{Aug. 2010 -- Dec. 2011}
				{ \small
				\begin{itemize}
					\resitem{Undergraduate researcher in the Electrical and Electronics department. Worked on video compression algorithms and character recognition in images.
				\end{itemize}
				}

	}\end{itemize}  % End Experience list


%%%%%%%%%%%%%%%%%%%%%%
\resheading{Teaching Experience}
	\vspace{-13pt}
	\begin{itemize}
		\item 
			\ressubheading{\href{https://www.coursera.org/course/compinvesting1}{Coursera}}{Atlanta, GA}{Teaching Assistant}{Aug. 2012 -- Present}
				{ \small
				\begin{itemize}
					\resitem{Course: Computational Investing - I. Created the class website, quizzes, programming assignments and video tutorials. The course has 75,000 students enrolled till now and was featured on 11 alive news and the AJC.}
				\end{itemize}
				}
		\item			
			\ressubheading{\href{https://www.gatech.edu}{Georgia Institute of Technology}}{Atlanta, GA}{Graduate Teaching Assistant}{Aug. 2012 -- Dec. 2012}
				{ \small				
				\begin{itemize}
					\resitem{Course: Machine learning for Trading. Took 3 guest lectures in the class on usage of QuantSoftware Toolkit. Created programming assignment and exams, conducted recitations and office hours for the students.}
				\end{itemize}
				}
		\item 
			\ressubheading{\href{http://www.bits-pilani.ac.in}{Birla Institute of Technology and Science}}{Pilani, India}{Teaching Assistant}{Aug. 2009 -- May 2010}
				{ \small
				\begin{itemize}
					\resitem{Teaching assistant for undergraduate courses Computer Programming 1, Digital Electronics and Engineering graphics. Conducted lab and recitation sessions, and helped students in office hours.
				\end{itemize}
				}

	}\end{itemize}  % End Experience list
%%%%%%%%%%%%%%%%%%%%%%

\resheading{Academic Projects}
	\vspace{-13pt}
	\begin{itemize}
		\item{\small \textbf{Portfolio Replication:} \small Designing a replication algorithm using machine learning, pattern recognition and statistical methods, applications include creating survivor bias free data and creating clones of hedge fund portfolios. }
			\vspace{-2pt}
		\item{\small \textbf{Quant Software Toolkit :} \small Open source quantitative analysis library in Python. Features include application of machine learning for finance, technical indicator analysis, trade simulation etc.   \url{www.wiki.quantsoftware.org}}
			\vspace{-2pt}
		\item{\small \textbf{Music Recommendation System:} \small Designed a recommendation system from the Yahoo Music database with over 1 Million users, 640,000 songs and over 300 million ratings, using Collaborative Filtering.}
			\vspace{-2pt}
		\item{\small \textbf{PCA, KPCA and ICA for Dimensionality Reduction :} \small Comparative study between PCA, KPCA and ICA dimensionality reduction algorithms for different classification tasks using SVM and Decision trees.}
			\vspace{-2pt}
		\item{\small \textbf{Computer Vision :} \small Implemented several computer vision algorithms such as Hough transforms, Disparity images, Camera calibration, Lucas and Kanade, Harris corners, Ransac, Particle filter based tracking and Activity recognition.}
	\end{itemize}
	
%%%%%%%%%%%%%%%%%%%%%%

\resheading{Publications}
	\vspace{-13pt}
	\begin{itemize}
		\item 
			{\small Sourabh Bajaj and Devaphanindra Kumar, \textit{3D Image control using MEMS sensors for Teaching Purposes}, 4th IEEE International conference of Electronics Computer Technology, 2012.}
			\vspace{-2pt}
		\item 
			{\small Sourabh Bajaj and Devaphanindra Kumar, \textit{Novel Approach to 3D gaming using MEMS Sensors}, 4th IEEE International conference of Electronics Computer Technology, 2012.}
			\vspace{-2pt}
		\item 
			{\small Sourabh Bajaj and Devaphanindra Kumar, \textit{Real time 3D Anaglyph Image Control Using MEMS Sensors}, Advanced Materials Research Journal, 2011.}
	\end{itemize}  % End Publications list
	
%%%%%%%%%%%%%%%%%%%%%%

\resheading{Awards and Achievements}
	\vspace{-13pt}
	\begin{itemize}
		\item 
			\textbf{Scholastic Achievements}
			\vspace{-5pt}
				{ \small
				\begin{itemize}
					\resitem{Full tution waiver for the Masters program at Georgia Tech.}
					\resitem{Merit scholarship(full tution waiver) for excellence in academic year 2009-2010.}
					\resitem{Winner of several programming competitions in College and High School.}
					\resitem{Top 2\% in National Informatics Olympiad, 2008.}
				\end{itemize}
				}
		\item 
			\textbf{Leadership}
			\vspace{-5pt}
				{ \small
				\begin{itemize}
					\resitem{Graduate Student Senate for computer science at Georgia Tech. Involved in the allocation of 1 million dollars between various different student organizations. 2012}
					\resitem{Reviewer for International Conference on Signal Processing, Computing and Control, 2012.}
					\resitem{Vice President, IEEE Student Chapter at BITS Pilani, 2011.}
					\resitem{Student Incharge, Anti-Ragging Commitee Boys Hostel, 2011.}
					\resitem{Student Union Representative, Sardar Patel Vidyalaya, 2008.}
				\end{itemize}
				}
	\end{itemize}
		
	% End Awards list
	
\end{document}
%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%

\resheading{Academic Projects}
	\vspace{-13pt}
	\begin{itemize}
%		\item{\small \textbf{Quant Software Toolkit :} \small Open source quantitative analysis library in Python. Written functions for mean variance optimization, event studies, Visualizers and portfolio simulators etc. 2012.}
%			\vspace{-2pt}
%		\item{\small \textbf{User Rating Prediction and Music Recommendation :} \small Designed a rating prediction system from the Yahoo Music database with 1 Million users and 640,000 songs. 2012}
%			\vspace{-2pt}
%		\item{\small \textbf{PCA, KPCA and ICA for Dimensionality Reduction :} \small Comparative study between PCA, KPCA and ICA for SVM and Decision trees, for Face Recognition, Handwritten Recognition and Arrhythmia detection. 2012}
%			\vspace{-2pt}
		\item{\small \textbf{Computer Vision :} \small Code for several computer vision algorithms such as Hough transforms, Disparity images, Camera calibration, Lucas and Kanade, Harris corners, Ransac and Particle filters etc. 2012}
			\vspace{-2pt}
		\item{\small \textbf{Video Compression :} \small Comparison of various video compression algorithms such as MPEG, H.263 and XYZ. 2011}
			\vspace{-2pt}
		\item{\small \textbf{Analgyph control using MEMS :} \small Real time control of an Anaglyph using accelerometers and gyroscopes. 2011}
			\vspace{-2pt}
		\item{\small \textbf{Economic Power Dispatch :} \small Algorithm for optimal solution to economic dispatch problem in power-systems. Implemented in Matlab to run for a N dimension load and M generator system. 2011}
			\vspace{-2pt}
		\item{\small \textbf{Automation of GAIL-DVPL Gas Pipeline :} \small Designed, Programmed and Tested PLC panels for the automation of a 600 km long, Gas authority of India Pipeline. 2010}
			\vspace{-2pt}
		\item{\small \textbf{Older Projects :}
			{ \small
			\vspace{-4pt}
				\begin{itemize}
					\resitem{Character Recognition using Neural Networks, 2010.}
					\resitem{Design of a Hospital Database Management System, 2010.}
					\resitem{Speed control of a Lift using 8086 microprocessor, 2009.}
					\resitem{Design of a hovercraft model, 2008.}
				\end{itemize}
				}
		}
	\end{itemize}
\end{document}

%Only Print References If Requested!  Maybe even put it in it's own page.  Must have same heading as first page.
%%%%%%%%%%%%%%%%%%%%%%
\newpage
\myheader
\resheading{References}
	\begin{center}
		\begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}  l l l }
			Toby Rummans & Eric Karl & Gordon Smith \\
			Entry Level Web Developer & Computer Science \& Engineering  & Technology Support Specialist \\ 
			\vspace{10pt} 
			Memolinkcorp & BYU-Idaho & BYU-Idaho \\ 
			[removed] & 525 South Center St. & 525 South Center St.  \\
			Denver, CO 80210 & Rexburg ID 83460 & Rexburg ID 83460 \\
			[removed] & (208) 496-3097 & (208) 496-2816 \\
		\end{tabular*}
	\end{center}
	
% \end{document}


% ADDITIONAL WORK EXPERIENCE NOT INCLUDED	OR OLD

		\item 
			\ressubheading{\href{http://www.rexburgmotorsports.com/}{Rexburg Motorsports}}{Rexburg, ID}{Computer Systems Administrator}{Aug. 2006 -- Oct. 2006}
				{ \footnotesize
				\begin{itemize}
	            			\resitem{Managed file and application servers running Windows 2003 Server}
	            			\resitem{Performed all levels of hardware and software systems support for 40 computers and 10 printers}
				\end{itemize}
				}

		\item 
			\ressubheading{Bresnan Communications}{Billings, MT}{Teir 1 Technical Support}{Jan. 2006 -- April 2006}
				{ \footnotesize
				\begin{itemize}
					\resitem{Provided Bresnan customers with technical support over the phone.}
					\resitem{Receieved training on resolving networking, cable TV, and VOIP issues.}
				\end{itemize}
				}

		\item 
			\ressubheading{Northwestern Energy}{Billings, MT}{Summer Gas/Electrical Engineer}{May 2004 -- April 2005}
				\begin{itemize}
					\resitem{Interned with full time Gas/Electrical Engineers.}
					\resitem{Documented, mapped, and marked city streetlights using MS Access, GTViewer, FRAMME, and CAD.}
				\end{itemize} 


%%%%%%%%%%%%%%%%%%%%%%%%
% GENERAL RESUME NOTES %
%%%%%%%%%%%%%%%%%%%%%%%%
Need to brush up on the skills section?  Here are some really good ideas:

- Communication: The ability to express and interpret ideas and convey knowledge. 
Skills like speaking effectively, writing concisely, listening attentively, expressing ideas, 
reporting information, editing, interviewing, and facilitating group discussion. 
 
- Research and Planning: The ability to search for specific knowledge and formulate a 
program for a definite course of action. Skills like forecasting, predicting, identifying 
issues, finding alternatives, gathering information, solving problems, setting goals, 
extracting information, and developing strategies. 
 
- Human Relations: The ability to apply interpersonal skills to resolve conflict, relate to 
people, and help people. Skills like providing support for others, listening, delegating 
with respect, representing others, asserting, developing rapport, and perceiving 
feelings. 
 
- Management, Organization, Leadership: The ability to supervise others and guide 
individuals and groups towards the completion of tasks. Skills like managing groups, 
selling ideas, making decisions, managing conflict, coordinating tasks, teaching, 
enlisting help. 

Source: 
http://www.squawkfox.com/2009/03/08/6-action-words-that-make-your-resume-rock/

Other Resources: 
http://www.tvmier.com/Resume_Education.html

