%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Sourabh Bajaj
\documentclass[margin,line]{resume}


%______________________________________________________________________________________________________________________
\begin{document}
\addtolength{\topmargin}{.1in}
\name{\huge Sourabh Bajaj}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    301, 10th Street NW, \#204C                   \hfill mobile: (404) 834 - 4787       \vspace{0mm}\\\vspace{0mm}%
    Georgia Institute of Technology, Atlanta, GA USA  \hfill e-mail: sourabhbajaj@gatech.com  \vspace{0mm}\\\vspace{-4.5mm}%


    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Objective}
    Seeking an Internship/Co-op position in the field of computer science. \\

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}
    \textbf{Georgia Institute of Technology}, Atlanta, GA \vspace{2mm}\\\vspace{1mm}% 
    \textsl{Master of Science, Computer Science (Machine Learning)} \hfill \textbf{ Aug 2012 -- Dec 2013}\vspace{-3mm}\\\vspace{-1mm}

    \textbf{Birla Institute of Technology and Science}, Pilani, India \vspace{2mm}\\\vspace{1mm}%
    \textsl{Bachelor of Engineering, Electrical and Electronics} \hfill \textbf{ Aug 2008 -- July 2012}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Cumulative GPA:  9.15/10 
    \end{list2}\vspace{-1.5mm}
    
    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Programming\\Skills} 
    Proficient : Python, Matlab, C, C++, Maxima, \LaTeXe, Git, SVN, Mac OS, Linux, Windows. \\
    Familiar : R, SQL, SQLite, XHTML, CSS, AutoCAD, Java, Arduino Programming. \\
    
    %__________________________________________________________________________________________________________________
    % Publications
    \section{\mysidestyle Publications}

    Sourabh Bajaj and Devaphanindra Kumar,
    ``3D Image control using MEMS sensors for Teaching Purposes'',
    \textsl{4th IEEE International conference of Electronics Computer Technology}, 2012.

    \vspace{-2mm}
    Sourabh Bajaj and Devaphanindra Kumar,
    ``Real time 3D Anaglyph Image Control Using MEMS Sensors'',
    \textsl{7th International conference on MEMS, NANO and Smart Systems}, published in Advanced Materials Research Journal, 2011.


    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}

    \textbf{Coursera}, Atlanta, USA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Teaching Assistant} \hfill \textbf{Aug 2012 -- Present}\\
    Teaching assistant for the class Computational Investing - Part 1. Involved in creating assignment, exams, content for the class. Creating class webpages and software support for the class. This class has 46,000 students enrolled currently. Also created several tutorial videos for the class.

    \textbf{Georgia Institute of Technology}, Atlanta, USA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Graduate Teaching Assistant} \hfill \textbf{Aug 2012 -- Present}\\
   Teaching assistant for the class Machine learning for Trading. Involved in creating assignment and exams, recitations on installation and usage of software (QSTK) used in the class. 

    \textsl{Graduate Research Assistant} \hfill \textbf{Aug 2012 -- Present}\\
    Research under Dr. Tucker Balch, work involves creation of various portfolio hedging algorithms for risk minimization. And application of machine learning for price forecasting.

    \textbf{Lucena Research}, Atlanta, USA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Summer Intern} \hfill \textbf{May 2012 -- July 2012}\\
    Development of proprietary algorithms for risk minimization, portfolio optimization and portfolio hedging. Designed a backtesting framework for strategy testing over historical data.

    \textbf{Georgia Institute of Technology}, Atlanta, USA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Visiting Scholar} \hfill \textbf{Jan 2012 -- May 2012}\\
    Design of a modern portfolio theory based optimizer, for optimal portfolio allocations for max return and minimum risk. Also created a visualization tool for analysis of various technical indicators.
\newpage
    \textbf{Birla Institute of Technology and Science}, Pilani, India \vspace{2mm}\\\vspace{1mm}%
    \textsl{Teaching Assistant} \hfill \textbf{August 2009 -- December 2011}\\
    Teaching assistant for undergraduate courses Digital Electronics and computer organization, Computer Programming and Engineering graphics. Conducted Lab session and invigilation of lab practicals.

    \textbf{Analog Devices}, Bengaluru, India \vspace{2mm}\\\vspace{1mm}%
    \textsl{Summer Intern} \hfill \textbf{May 2011 -- July 2011}\\
    Real time 3D image control using MEMS sensors, it involved designing of a low cost prototype that can be used to control a Anaglyph image in real time using MEMS based inertial sensors. 

    \textbf{Larsen and Toubro}, Mumbai, India \vspace{2mm}\\\vspace{1mm}%
    \textsl{Summer Intern} \hfill \textbf{May 2010 -- July 2010}\\
    Automation of a 600km Gas Pipeline, the project involved design, programming and testing of PLC panels for the installation of a Gas authority of India Pipeline.

    %__________________________________________________________________________________________________________________
    % Honours and Awards
    \section{\mysidestyle Honors and\\Awards} 
    Elected as Graduate Student Senate member for computer science at Georgia Tech, 2012.\vspace{1mm}\\%
    Vice President of IEEE student chapter at BITS Pilani, 2011.    \vspace{1mm}\\%
    Student In-charge of Anti-Ragging committee of Boys Hostel- Bhagirath Bhawan, 2011.  \vspace{1mm}\\%
    Merit Scholarship, Birla Institute of Technology and Science, Pilani, 2009.              \vspace{1mm}\\%
    Selected in Top 5 out of 100+ entries in BITS Epsilon a B-Plan competition, Pilani, 2008.          \vspace{1mm}\\%
    In Top 2\% in over 10,000+ participants, National Cyber Olympiad in year, 2008.   \\%
 

    %__________________________________________________________________________________________________________________
    % Major Courses
    \section{\mysidestyle Major\\Courses}
    Current : Machine Learning, Machine Learning for Trading, Artificial Intelligence, Computer Vision. \vspace{1mm}\\
    Multi Robot Systems, Digital Electronics and Computer Organization,Image Processing, Microprocessor programming, Circuits and
    Signals, Computer Programming, Basic Electrical sciences, Computer Networks, Control systems, 
    Data communication and Networks. \\     

    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Class\\Projects}

    Projects apart from work done during the Internship, or under confidentiality agreements.

    \textbf{PCA, KPCA, ICA for Dimensionality Reduction} \hfill \textbf{August 2012 -- October 2012}\\
    Comparative study of PCA, KPCA and ICA algorithms for dimensionality reduction for Handwritten digits, Face recognition and Arrhythmia detection for SVM and Decision Trees.

    \textbf{Real time Video compression} \hfill \textbf{August 2011 -- December 2011}\\
    Research under Dr. J.L. Raheja in Central Electronics Engineering Research Institute. Study of various video compression
    algorithms, including MPEG, H.264, XYZ.

    \textbf{Solution of Economic Dispatch problem} \hfill \textbf{January 2011 -- May 2011}\\
    An algorithm was designed to obtain the solution to economic dispatch problem in power-systems. It was implemented in Matlab
    to run for a N dimension load and generator system.
    
    \textbf{Character Recognition using Neural networks} \hfill \textbf{August 2010 -- December 2010}\\
    Implementation of a character recognition system in MATLAB. It was designed to filter any alphabet with a noise margin of 
    30\%. Understanding of learning of Neural networks, backpropogation algorithms was obtained.

    \textbf{Misc. Projects} \hfill \textbf{March 2009 -- December 2011}\\
    Implementation of DC-DC buck converter. Design of Hospital based Data Management system in Access. Hovercraft model Design.
    Line following Robot. Speed control of a Lift using 8086 Microprocessor.


    %__________________________________________________________________________________________________________________
    % Referees
%    \section{\mysidestyle Referees} 
%    {\sl Available on request.}



%______________________________________________________________________________________________________________________
%\section{\mysidestyle Referees} 
%
%     \begin{itemize}
%      \item Dr. Tucker Balch, Associate Professor, Georgia Institute of Technology.
%      \item Erez Katz, CEO, Lucena Research.
%      \item Dr. H. D. Mathur, Associate Professor, BITS, Pilani.
%      \item Dr. Sapna Sharma, Associate Professor, BITS, Pilani.
%      \item Mr. Devaphanindra Kumar, Design Engineer, Analog Devices.
%     \end{itemize}


%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

